An Experimental Analysis of the Influence of the Precision of Parameters in an Artificial Neural Network

### 2025-11-12 paper/main.tex
weiter

\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{caption}
\usepackage{csquotes}
\usepackage{float}
\usepackage{derivative}
\usepackage{subcaption}

@@

try out mixed-precision training, using a mix of Half-Precision Floating Point
(FP16) and Single-Precision Floating Point (FP32) formats. On top of that, we
experiment with different types of gradient clipping, like global norm clipping
and value clipping, to see how they affect training stability and final
accuracy. \\\\ Even though we use relatively simple network architectures and
datasets, our results show that neural networks are quite robust to
low-precision settings. In some cases, we were able to round weights to just
three decimal digits and still get nearly the same accuracy as the
full-precision version. These findings show that it is possible to
significantly reduce the memory and compute needs of neural networks without
losing much performance. This makes them more practical for use in low-resource
settings. It also opens the door for more advanced techniques that combine
quantization, pruning, and precision-aware training to build highly efficient
models for real-world applications.

@@

\begin{equation}\label{eq:activation}
	a = \omega^\top x + b,\quad \hat{y} = \sigma(a),
\end{equation}

@@

\newpage
\section{Results}
In the first experiment, every floating-point tensor that is used inside the
training loop was converted to a lower precision data type. This therefore
includes the weights and biases, activations, gradients, optimizer states, etc.
The types tried were FP64, FP32, and FP16.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{caption}
\usepackage{csquotes}
\usepackage{float}
\usepackage{derivative}
\usepackage{subcaption}
\usepackage{bbm}

@@

try out mixed-precision training, using a mix of Double-Precision Floating
Point (FP64), Half-Precision Floating Point (FP16) and Single-Precision
Floating Point (FP32) formats. On top of that, we experiment with different
types of gradient clipping, like global norm clipping and value clipping, to
see how they affect training stability and final accuracy. \\\\ Even though we
use relatively simple network architectures and datasets, our results show that
neural networks are quite robust to low-precision settings. In some cases, we
were able to round weights to just three decimal digits and still get nearly
the same accuracy as the full-precision version. These findings show that it is
possible to significantly reduce the memory and compute needs of neural
networks without losing much performance. This makes them more practical for
use in low-resource settings. It also opens the door for more advanced
techniques that combine quantization, pruning, and precision-aware training to
build highly efficient models for real-world applications.

@@

\begin{equation}\label{eq:activation}
	a=\omega^\top x+b,\quad\hat{y}=\sigma(a)
\end{equation}

@@

\section{Results}
In the first experiment, every floating-point tensor that is used inside the
training loop was converted to a lower precision data type. This therefore
includes the weights and biases, activations, gradients, optimizer states, etc.
The types tried were FP64, FP32, and FP16.
